A highly-available move operation for replicated trees

### 2019-06-17 paper/move-op.tex
add isabelle lemmas

% DPM: add efficient_ancestor_simp here

@@

% DPM: add efficient_do_op_simulates here

@@

%DPM: add efficient_apply_ops_simulates here

@@

% DPM: add efficient_apply_ops_commutes and efficient_apply_ops_acyclic here

>>>>

% DPM: add efficient_ancestor_simp here
\begin{isabelle}
\isacommand{theorem}\isamarkupfalse%
\ efficient{\isacharunderscore}ancestor{\isacharunderscore}simp\ {\isacharbrackleft}code{\isacharbrackright}{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isacartoucheopen}efficient{\isacharunderscore}ancestor\ t\ p\ c\ {\isasymlongleftrightarrow}\isanewline
\ \ \ \ \ \ \ \ \ \ {\isacharparenleft}case\ hm{\isachardot}lookup\ c\ t\ of\isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ None\ {\isasymRightarrow}\ False\isanewline
\ \ \ \ \ \ \ \ \ \ \ \ {\isacharbar}\ Some\ {\isacharparenleft}m{\isacharcomma}\ a{\isacharparenright}\ {\isasymRightarrow}\isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ a\ {\isacharequal}\ p\ {\isasymor}\ efficient{\isacharunderscore}ancestor\ t\ p\ a{\isacharparenright}{\isacartoucheclose}
\end{isabelle}

@@

% DPM: add efficient_do_op_simulates here
\begin{isabelle}
\isacommand{lemma}\isamarkupfalse%
\ efficient{\isacharunderscore}do{\isacharunderscore}op{\isacharunderscore}simulates{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isadigit{1}}{\isacharcolon}\ {\isacartoucheopen}t\ {\isasympreceq}\ T{\isacartoucheclose}\isanewline
\ \ \ \ \isakeyword{and}\ {\isadigit{2}}{\isacharcolon}\ {\isacartoucheopen}efficient{\isacharunderscore}do{\isacharunderscore}op\ {\isacharparenleft}oper{\isacharcomma}\ t{\isacharparenright}\ {\isacharequal}\ {\isacharparenleft}log{\isadigit{1}}{\isacharcomma}\ u{\isacharparenright}{\isacartoucheclose}\isanewline
\ \ \ \ \isakeyword{and}\ {\isadigit{3}}{\isacharcolon}\ {\isacartoucheopen}do{\isacharunderscore}op\ {\isacharparenleft}oper{\isacharcomma}\ T{\isacharparenright}\ {\isacharequal}\ {\isacharparenleft}log{\isadigit{2}}{\isacharcomma}\ U{\isacharparenright}{\isacartoucheclose}\isanewline
\ \ \isakeyword{shows}\ {\isacartoucheopen}log{\isadigit{1}}\ {\isacharequal}\ log{\isadigit{2}}\ {\isasymand}\ u\ {\isasympreceq}\ U{\isacartoucheclose}
\end{isabelle}

@@

%DPM: add efficient_apply_ops_simulates here
\begin{isabelle}
\isacommand{lemma}\isamarkupfalse%
\ efficient{\isacharunderscore}apply{\isacharunderscore}ops{\isacharunderscore}simulates{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isadigit{1}}{\isacharcolon}\ {\isacartoucheopen}efficient{\isacharunderscore}apply{\isacharunderscore}ops\ opers\ {\isacharequal}\ {\isacharparenleft}log{\isadigit{1}}{\isacharcomma}\ u{\isacharparenright}{\isacartoucheclose}\isanewline
\ \ \ \ \isakeyword{and}\ {\isadigit{2}}{\isacharcolon}\ {\isacartoucheopen}apply{\isacharunderscore}ops\ opers\ {\isacharequal}\ {\isacharparenleft}log{\isadigit{2}}{\isacharcomma}\ U{\isacharparenright}{\isacartoucheclose}\isanewline
\ \ \isakeyword{shows}\ {\isacartoucheopen}log{\isadigit{1}}\ {\isacharequal}\ log{\isadigit{2}}\ {\isasymand}\ u\ {\isasympreceq}\ U{\isacartoucheclose}
\end{isabelle}

@@

% DPM: add efficient_apply_ops_commutes and efficient_apply_ops_acyclic here
\begin{isabelle}
\isacommand{theorem}\isamarkupfalse%
\ efficient{\isacharunderscore}apply{\isacharunderscore}ops{\isacharunderscore}commutes{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isadigit{1}}{\isacharcolon}\ {\isacartoucheopen}set\ ops{\isadigit{1}}\ {\isacharequal}\ set\ ops{\isadigit{2}}{\isacartoucheclose}\isanewline
\ \ \ \ \isakeyword{and}\ {\isadigit{2}}{\isacharcolon}\ {\isacartoucheopen}distinct\ {\isacharparenleft}map\ move{\isacharunderscore}time\ ops{\isadigit{1}}{\isacharparenright}{\isacartoucheclose}\isanewline
\ \ \ \ \isakeyword{and}\ {\isadigit{3}}{\isacharcolon}\ {\isacartoucheopen}distinct\ {\isacharparenleft}map\ move{\isacharunderscore}time\ ops{\isadigit{2}}{\isacharparenright}{\isacartoucheclose}\isanewline
\ \ \ \ \isakeyword{and}\ {\isadigit{4}}{\isacharcolon}\ {\isacartoucheopen}efficient{\isacharunderscore}apply{\isacharunderscore}ops\ ops{\isadigit{1}}\ {\isacharequal}\ {\isacharparenleft}log{\isadigit{1}}{\isacharcomma}\ t{\isacharparenright}{\isacartoucheclose}\isanewline
\ \ \ \ \isakeyword{and}\ {\isadigit{5}}{\isacharcolon}\ {\isacartoucheopen}efficient{\isacharunderscore}apply{\isacharunderscore}ops\ ops{\isadigit{2}}\ {\isacharequal}\ {\isacharparenleft}log{\isadigit{2}}{\isacharcomma}\ u{\isacharparenright}{\isacartoucheclose}\isanewline
\ \ \isakeyword{shows}\ {\isacartoucheopen}log{\isadigit{1}}\ {\isacharequal}\ log{\isadigit{2}}\ {\isasymand}\ hm{\isachardot}lookup\ c\ t\ {\isacharequal}\ hm{\isachardot}lookup\ c\ u{\isacartoucheclose}\isanewline
\isanewline
\isacommand{theorem}\isamarkupfalse%
\ efficient{\isacharunderscore}apply{\isacharunderscore}ops{\isacharunderscore}acyclic{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isadigit{1}}{\isacharcolon}\ {\isacartoucheopen}efficient{\isacharunderscore}apply{\isacharunderscore}ops\ ops\ {\isacharequal}\ {\isacharparenleft}log{\isacharcomma}\ t{\isacharparenright}{\isacartoucheclose}\isanewline
\ \ \isakeyword{shows}\ {\isacartoucheopen}{\isasymnexists}n{\isachardot}\ efficient{\isacharunderscore}ancestor\ t\ n\ n{\isacartoucheclose}
\end{isabelle}
